Gammapy: A Python package for gamma-ray astronomy

### 2023-03-10 src/ms-review.tex

%% \gammapy: concept and goals
%%% Question: starting date? Is is relevant, what is the real start?
The \gammapy project was started following the model of \astropy, with the objective of building a common
software library for very high-energy \gammaray data analysis \citep{gammapy_2015}. 
The core of the idea is illustrated in Figure~\ref{fig:big_picture}. The various \gammaray instruments
can export their data to a common data format (\gadf) and then these data can be combined and
analysed using a common software library.
The \gammapy is package an independent community-developed software project, it has been selected to be the core library for the Science Analysis tools of CTAO
but also involves contributors associated to other instruments.
The \gammapy package is built on the scientific Python ecosystem: it uses \numpy~\citep{numpy} for n-dimensional data
structures, \scipy~\citep{2020SciPy-NMeth} for numerical algorithms, \astropy~\citep{astropy} for
astronomy-specific functionality, \iminuit~\citep{iminuit} for numerical minimisation
and \matplotlib~\citep{matplotlib} for visualization.

>>>>

%% \gammapy: concept and goals
%%% Question: starting date? Is is relevant, what is the real start?
The \gammapy project was started following the model of \astropy, with the objective of building a common
software library for very high-energy \gammaray data analysis \citep{gammapy_2015}. 
The core of the idea is illustrated in Figure~\ref{fig:big_picture}. The various \gammaray instruments
can export their data to a common data format (\gadf) and then these data can be combined and
analysed using a common software library.
The \gammapy package is an independent community-developed software project, it has been selected to be the core library for the Science Analysis tools of CTAO
but also involves contributors associated to other instruments.
The \gammapy package is built on the scientific Python ecosystem: it uses \numpy~\citep{numpy} for n-dimensional data
structures, \scipy~\citep{2020SciPy-NMeth} for numerical algorithms, \astropy~\citep{astropy} for
astronomy-specific functionality, \iminuit~\citep{iminuit} for numerical minimisation
and \matplotlib~\citep{matplotlib} for visualization.
